Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-03-25 chapters/paper1_new.tex
Rewriting paper 1 chapter

% Anisotropic particles, when adsorbed at liquid interfaces, induce
% shape-dependent capillary interactions that can have a distinct effect
% on the microstructure of emulsions
% \cite{loudet_capillary_2005,loudet_self-assembled_2009}. For instance,
% Madivala et
% al.~\cite{madivala_exploiting_2009,madivala_self-assembly_2009} found
% that emulsion stability can be significantly enhanced by ellipsoidal
% particles. Additionally, capillary interactions can lead to direct
% assembly of anisotropic particles
% \cite{bowden_self-assembly_1997,lewandowski_orientation_2010,stebe_oriented_2009,botto_capillary_2012}.
% Ellipsoidal particles can rotate and migrate on curved surfaces
% \cite{cavallaro_curvature-driven_2011}, where the interface curvature
% acts as an external field that controls the orientation and placement
% of particles \cite{furst_directing_2011}. Anisotropic particles at
% fluid interfaces were considered in Monte Carlo simulations by Bresme
% et al. to test the accuracy of thermodynamic models for the free
% energy as a function of the particle-fluid interactions, particle
% size, and orientation
% \cite{bresme_orientational_2007,bresme_computer_2008}. Harting and
% co-workers \cite{gunther_lattice_2013,gunther_timescales_2014} have
% performed lattice Boltzmann simulations of anisotropic particles at
% liquid interfaces and in emulsions. They found that anisotropic
% particles affect the dynamics of emulsion formation by introducing two
% additional timescales associated with particle rotation. Following
% initial adsorption, particles rotate to align their larger
% cross-section with the interface. When jamming sets in, capillary
% interactions cause the particle to re-orient in the interface leading
% to prolonged coarsening at long timescales. Due to the larger aspect
% ratio, ellipsoidal particles can stabilize a larger interface area
% leading to smaller domain sizes. Hijnen et
% al.~\cite{hijnen_bijels_2015} experimentally realized bijels
% stabilized by colloidal rods and analyzed their effect on the
% interface and domain morphology. Their experiments confirmed that
% jamming occurs at lower interface separations than for spherical
% particles with the same volume fraction. Moreover, they observed that
% the overall structure remains isotropic and attributed this to the
% rapid jamming of the rods. Additionally, they found that some rods
% tilted out of the interface due to the compression induced by domain
% coarsening.

% Particle-stabilized emulsions can be made responsive to external
% magnetic fields by magnetic particles
% \cite{melle_pickering_2005,zhou_magnetic_2011}. An external field can
% then be used to control the stability of the emulsion
% \cite{melle_pickering_2005} and the self-assembly of particles
% \cite{dassanayake_structure_2000,leunissen_directing_2009}. The tendency
% of anisotropic particles to adopt distinct orientations gives rise to an
% orientation transition when an external field is applied
% \cite{morgan_understanding_2012,davies_interface_2014,davies_dipolar_2015}.
% Magnetic fields thus offer a means to control the capillary interactions
% of ellipsoidal particles at an interface. For bijels stabilized by
% spherical magnetic particles, simulations by Kim et
% al.~\cite{kim_bijels_2010} revealed that magnetic fields do not have a
% significant effect on the microstructure of bijels. In contrast, Carmack
% and Millett \cite{carmack_tuning_2018} demonstrated that the structure
% of thin-film bijels stabilized by dielectric particles can change
% drastically when an external electric field is applied. The dielectric
% contrast of the particles induces polar interactions that cause liquid
% domain alignment leading to percolating cylindrical domains in the
% thin-film bijel. In addition, they found that particle chains can act as
% nucleation sites for phase separation. This suggests that anisotropic
% interactions can have a considerable effect on the phase separation and
% the resulting emulsion morphology and may offer a means to control the
% size and shape of liquid domains.

@@

Bijels can be used as emulsion templates for porous materials with
applications including drug delivery, water desalination, and battery
electrodes
\cite{vanoli_bijels_2022, chen_pore-scale_2022, lu_controllable_2020, garcia_scalable_2019}.
The transport properties of porous materials depend on the porosity and
tortuosity of the void space and can be linked to the phase-separated
morphology of the bijel template. Therefore, We study the domain size
and tortuosity of the phase morphology of bijels stabilized by
anisotropic particles. In particular, We investigate the effect of
magnetic particles on the microstructure of bijels that are formed in
external magnetic fields. We simulated bijels with a particle volume
fraction of \(\phi_p=0.15\) and varied the magnetic flux density such
that the Bond numbers varies in the range \(0\le\bar{B}\le1\).
In this work, We use a fixed particle volume fraction and focus on the dependence of the 
bijel structure on the magnetic field. Bijels with varying particle loading and surface tension 
and have been studied elsewhere in the literature, e.g., by Hijnen et al.\cite{hijnen_bijels_2015} 
and Jansen and Harting\cite{jansen_bijels_2011}.

@@

Figure \ref{fig:microstructure_viz} shows snapshots of the bijel
microstructure observed at different times with and without an external
magnetic field. The figure illustrates how anisotropic particles align
with the direction of the magnetic field. As the particles reorient,
they can deform the interface which thus responds by rearrangements
including reorientation and domain coalescence or breakup. This results
in apparently larger domain sizes for bijel formation in magnetic
fields. The quantitative effect on the bijel morphology, and domain size
in particular, is analyzed in the following sections.

\subsection{Structure factor and domain size of magnetically responsive bijels}

In LB simulations of spinodal decomposition, a characteristic length
scale can be obtained from the structure factor, defined in Section \ref{section:domain_size}. \cite{kendon_3d_1999,kendon_inertial_2001} 
It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
averaged structure factor is subject to poor statistics in the low \(k\)-shells, where the average \(|\vec{k}|\) of the 
lattice sites differs from the nominal shell radius. Additionally, the measurement of \(L(t)\) in simulations with
periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
We cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
\cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ we plot the structure factor of the structures in
Figure \ref{fig:structure_factor}.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/results/paper1/structure_factor.png}
    \caption{Scaling plot of the dynamic structure factor $S(k,t)$ for different particle shapes $\alpha$ and at different 
            magnetic field strength $\bar{B}$. The structure factor is plotted at four different timesteps for each case. The good data collapse shows that the 
            bijel formation is driven by spinodal decomposition. The decay to the right of the peak is reasonably well described by Porod's law $S(k)\sim k^{-4}$.}
    \label{fig:structure_factor}
\end{figure*}

Figure \ref{fig:structure_factor} shows the scaling of the dynamic
structure factor \(S(k,t)\). The data collapse is good, albeit
deviations from dynamic scaling are present at smaller length scales.
The decay to the right of the maximum is reasonably well described by
Porod's law \(S(k)\sim k^{-4}\) indicating scattering off a nearly flat
interface. These results are in line with the scaling results by Kendon
et al.~\cite{kendon_3d_1999, kendon_inertial_2001} for spinodal
decomposition of binary fluids, which suggests that the formation of
bijels is primarily driven by the separation dynamics of the fluids. The
effect of the suspended particles only comes into play once larger
domains have formed and the coarsening interface reduces the accessible
area to the point where the particles start interacting. The onset of
particle interactions and subsequent jamming leads to a fairly sudden
slow-down of domain growth, as can be observed in the time evolution of
the domain size shown in Figure \ref{fig:domain_size}.

The domain size \(L_1\) obtained from the spherically averaged structure
factor initially shows a power law behavior very close to
\(L_1\sim t^{2/3}\). A nonlinear curve fit of the function
\(b(t-t_0)^a\) to the interval \(t\in[0,\ 3\cdot10^5\Delta x]\) yields
the exponents \(a=0.6448\) for spherical particles, \(a=0.6083\) for
oblate particles with aspect ratio \(\alpha=0.5\), and \(a=0.652\) for
prolate ellipsoids with aspect ratio \(\alpha=2\). These values are in
good agreement with the exponent \(a=2/3\) that is expected in an
inertial scaling regime, where the characteristic velocity \(U=dL/dt\)
scales with the characteristic length scale
\(U\sim \sqrt{\sigma/(\rho L)}\), leading to \(L \sim t^{2/3}\). After
around 30,000 to 40,000 time steps, the domain growth starts slowing
down and approaches a plateau at \(L_1\approx 200\Delta x\) for
spherical particles, \(L_1\approx 180\Delta x\) for the prolate
particles, and \(L_1\approx 170\Delta x\) for the oblate particles.
Interestingly, the alternative domain size measure \(L_d\) obtained from
the second moments of the 3D structure factor does not show the same
power law behavior. The rate of increase of \(L_d\) is substantially
smaller than that of \(L_1\), with a fitted exponent in the range of
0.12 to 0.20. The increase of \(L_d\) levels of earlier and reaches a
plateau around \(L_d\approx 70\Delta x\) for all three particle aspect
ratios. While dynamic scaling allows different measures of the
characteristic length scale to vary by a prefactor, the deviation from
the expected power law of both viscous and inertial scaling indicates
that the second moment of the 3D structure factor does not yield a
proper characteristic length scale. %, contrary to what has been assumed in
%previous works \cite{jansen_bijels_2011, gunther_timescales_2014}.
If one interprets the moments of the structure factor as moments of a
probability distribution, then the second moment of the 3D structure
factor is equivalent to the ratio of the fourth and second moments of
the spherically averaged structure factor (due to the factor \(k^2\) in
the volume integral). Hence \(L_d\) is perhaps better interpreted as
describing the shape of the structure factor (similar to kurtosis, but
not exactly the same) rather than a characteristic length scale.
Nevertheless, the second moments \(L_\beta\) provide separate measures
for the three Cartesian directions and can thus reveal anisotropy of the
domain morphology.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/results/paper1/domain_size.png}
\caption{Time dependence of the average domain size of the bijel for different particles shapes $\alpha$ and at different magnetic 
         field strength $\bar{B}$. $L_1$ denotes the domain size obtained from the first moment of the spherical average structure 
         factor, and $L_d$ denotes the domain size obtained from the second moment of the 3D structure factor. The increase roughly 
         follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition.}
\label{fig:domain_size}
\end{figure*}

\subsection{Effect of magnetic field on bijel formation}

@@

At first glance, the time-dependence of the domain size in Figure 
\ref{fig:domain_size} suggests that the domain size is not strongly
affected by the external magnetic field. In Figure \ref{fig:D2a_B}a) we
plotted the domain size measure \(L_d\) normalized by \(R\), the larger
of the two radii of the ellipsoidal particles. The data points represent
the domain size measured at the final time step and averaged over three
independent simulation runs with the same parameters. The normalization
with the particle radius makes it apparent that the ellipsoidal
particles reduce the domain size of bijels. This observation is in line
with observations by Günther et al.~\cite{gunther_timescales_2014} and
indicates that -- relative to their volume -- ellipsoidal particles
stabilize a larger interface area than spherical particles. This is due
to the larger cross-sectional area of ellipsoidal particles at the same
volume. Furthermore, steric constraints prevent anisotropic particles to
pack less densely in the interface than spherical particles, as we will
discuss in more detail below.

The magnetic field does have an effect on the directional
domain size as shown in Figure \ref{fig:D2a_B} where we plotted the
domain size in the direction parallel and perpendicular to \(\vec{B}\)
separately. We find that for prolate particles, the domain size in the
parallel direction increases with the field strength up to approximately
three particle radii for the largest field, while the perpendicular
domain size stays constant. This trend is reversed for oblate particles
for which the domain size in the parallel direction decreases slightly
with field strength while the perpendicular domain size increases by
approximately four particle radii. Without a field, prolate
particles lead to smaller domain size than both spherical and oblate
particles, whereas they increase the domain size when the bijel forms under the
influence of a magnetic field. The anisotropy is due to the alignment of
ellipsoidal particles which leads to a closer packing within the
interface akin to nematic ordering. The difference between oblate and
prolate particles is caused by the orientation of the magnetic dipole
moment \(\vec{m}\) along the symmetry axis of the particles. In our
model, \(\vec{m}\) is aligned with the larger axis of prolate
ellipsoids, whereas it is aligned with the smaller axis of oblate
ellipsoids. Hence \(\vec{m}\) lies in the plane of the larger
cross-section of prolate particles while \(\vec{m}\) is perpendicular to
the larger cross-section of oblate particles. We thus expect that
alignment of the particles with the magnetic field \(\vec{B}\)
facilitates closer packing perpendicular to the field for prolate
particles, and parallel to the field for oblate particles. The
increase/decrease of domain size levels off at intermediate field
strength and further increases of the field have no additional effect.

@@

\begin{figure*}
\centering
\includegraphics[scale = 0.4]{figures/results/paper1/tortuosity_compare.png}
\caption{Dependence of the tortuosity on the magnetic field strength $\bar{B}$ for different particle shapes $\alpha$. 
         Different components of the tortuosity tensor show the anisotropy for oblate and prolate particles.}
\label{fig:tau_B}
\end{figure*}

The anisotropy of domain size suggests that the magnetic field
influences the bijel morphology at the microscale. To investigate
whether these structural changes have an effect on macroscopic
transport properties, we also characterized the tortuosity of the
bijels. Various definitions of tortuosity have been proposed in the
literature \cite{dasilva_tortuosity_2022}, including geometric,
diffusional, and hydraulic tortuosity. Here we use the diffusional
tortuosity $\tau= \frac{\epsilon D}{D_{\text{eff}}}$, i.e., the ratio of the 
effective diffusivity $D_{\text{eff}}$ and the intrinsic diffusivity
$D$. We calculate the tortuosity using the procedure detailed in Section \ref{section:tortuosity}

Figure \ref{fig:tau_B} shows the results for the tortuosity as a
function of the applied magnetic flux for the three particle aspect
ratios. In the absence a magnetic field, the three aspect ratios lead to
a similar tortuosity around $\tau\approx 1.5$, slightly larger than
the tortuosity predicted by the Bruggeman relation
\(\tau=\epsilon^{-0.5}=1.41\) for equal volume fractions
\(\epsilon=0.5\) of the phases
\cite{bruggeman1935tortuosity, tjaden_origin_2016}. The observed
tortuosity is consistent with simulations of gyroid structures by Luo et
al., who found diffusive tortuosities in the range from 1.48 to 1.73
\cite{luo_macroscopic_2020}. Figure \ref{fig:tau_B} shows that in an
applied magnetic field, the tortuosity of bijels stabilized by
anisotropic particles (\(\alpha\neq1\)) becomes anisotropic as well.
Oblate particles (\(\alpha=0.5\)) lead to an increase of the tortuosity
\(\tau_\parallel\) in the direction of the magnetic field while the
tortuosity in the direction perpendicular to the magnetic field remains
around \(\tau_\parallel\approx1.5\). Conversely, prolate particles
(\(\alpha=2\)) lead to an increase of the tortuosity in the direction
perpendicular to the magnetic field, while the tortuosity in the
parallel direction slightly decreases with increasing field strength. In
both cases, the changes in tortuosity are consistent with the
anisotropic domain size and the alignment of particles with the magnetic
field. For prolate particles, the longer axis is aligned with the
magnetic moment and induces larger domain size and lower tortuosity in
this direction. The results show that the magnetic field has a
noticeable effect on the tortuosity of the bijel. We observe that the
largest change of tortuosity is measured at intermediate field strength
\(\bar{B}=0.5\). This suggests that the competition of interfacial and
magnetic forces and the resulting alignment of particles and liquid
domains induces morphological changes that are more complex than a
monotonic increase or decrease. We therefore turn to investigate the
microstructural changes within the bijel morphology in more detail.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{figures/results/paper1/coarsening_vel.png}
\caption{Time-dependence of the coarsening velocity $u_L$ for different particles shapes $\alpha$  
and at different magnetic field strength $\bar{B}$. The different components of the coarsening velocity 
show that the jamming time is different in the direction parallel and perpendicular to the magnetic field.}
\label{fig:coarsening_velocity}
\end{figure*}

Figure \ref{fig:coarsening_velocity} shows the coarsening speed in the directions parallel and perpendicular to the applied magnetic field. 
The data confirms that for spherical particles, domain coarsening remains isotropic. We observe a higher coarsening speed initially which slows 
at later times when the particles begin to jam. This indicates that the
coarsening is subject to different time scales, as reported previously
by Harting and co-workers \cite{gunther_timescales_2014}. Reeves et
al.~\cite{reeves_particle-size_2015} have pointed out that bijel
formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through 
depercolation. In our simulations, however, we have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations 
by Stratford et
al.~\cite{stratford_colloidal_2005} and Jansen et al.~\cite{jansen_bijels_2011}.

For ellipsoidal particles, our data clearly shows that an\-isotropic
domain coarsening arises in magnetic fields.  For oblate particles
(\(\alpha=0.5\)), the coarsening speed in the direction perpendicular
to the field increases with increasing magnetic field strength.
Jamming in this direction appears to be delayed compared with the
direction parallel to the field. The coarsening speed in the parallel
direction remains comparable to the case without an applied magnetic
field. This anisotropic behavior of the coarsening speed reverses for
prolate particles, where the coarsening speed in the direction parallel to the field increases with increasing field strength, and jamming in this direction
is delayed compared with the perpendicular direction. In addition, we observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in. These results suggest that the coarsening near the jamming time is affected by a mechanism that depends on the applied magnetic field and causes the anisotropic
behavior. This mechanisms involves the re-orientation of anisotropic
particles and their alignment relative to the direction of the
magnetic field. To confirm this hypothesis, we analyze the
orientational order of the particles and their alignment relative to
the magnetic field and the interface, respectively.

@@

The primary effect of the magnetic field is the torque it exerts on the
magnetic dipole of the particles. This torque rotates the particles
towards the direction of the magnetic field. The alignment of the
particles with the field direction can be clearly observed in the
simulation snapshots shown in Figure \ref{fig:packing_viz}. While the
particles are oriented randomly in the interface in the absence of a
magnetic field (\(\bar{B}=0\)), the magnetic field induces orientational
order of the magnetic dipoles (shown for \(\bar{B}=1\)).

@@

To measure the particle alignment quantitatively, we computed the
nematic order tensor using the method detailed in Section \ref{section:nematic_order_parameter} 
Figure \ref{fig:nematic_time} shows the time evolution of the nematic
order parameter \(S\) for the three different particle aspect ratios
\(\alpha\) and varying magnetic field strength \(\bar{B}\). The onset of
orientational order is nearly instantaneous and increases with
increasing field strength. For magnetic flux densities
\(\bar{B}\ge0.5\), the nematic order parameter saturates at
\(S\approx 1.0\) towards the end of the simulation. For the prolate
particles (\(\alpha=2.0\)), we observe a shoulder at around
\(10^4\Delta t\) and an intermittent plateau. The occurrence of this
plateau coincides with the slowed decay of the coarsening speed in Figure
\ref{fig:coarsening_velocity}. This change in the orientational ordering
is even more distinct for the oblate particles, where the nematic order
decays intermittently before it increases again. The intermittent decay
for oblate particles, and the plateau for prolate particles, correlate
with the delayed onset of jamming in the direction perpendicular and
parallel to the magnetic field, respectively. These observations can be
interpreted as follows: The magnetic field aligns the particles with the
direction of the magnetic field early during the simulation. Due to this
alignment, the steric constraints between particles adsorbed at the
interface are reduced which allows further coarsening of the interfacial
area. However, during coarsening, the interfaces may re-orient
themselves and cause a capillary torque on the particles that competes
with the magnetic torque. This competition intermittently perturbs the
nematic order of the particles leading to the observed decay and plateau
of the nematic order parameter. Accordingly, the decay of \(S\) is most
pronounced at the weakest magnetic field \(\bar{B}=0.2\). To further corroborate 
this mechanism, We plot the time evolution of the orientational order of the interfaces.

\begin{figure}
\centering
\includegraphics[scale = 0.4]{figures/results/paper1/interface_nematic.png}
\caption{Time-dependence of the interface nematic order for oblate ($\alpha=0.5$) and prolate ($\alpha=2$) particles at different magnetic field strength $\bar{B}$. The interface alignment tends to increase with increasing field strength. The rate of increase becomes larger around $10^4$ timesteps, indicating the alignment of the interfaces due to capillary interactions with the particles.}
\label{fig:interface_nematic}
\end{figure}

The results for the interface nematic order parameter $S_{\text{int}}$
are shown in Figure \ref{fig:interface_nematic}. The nematic interface
alignment increases over time and the rate of increase appears to be
higher for larger magnetic field strength $\bar{B}$. In all cases, the
final value of $S_{\text{int}}$ is below 0.5 indicating that the
tortuous structure of the interface is maintained in the presence of
magnetic fields. This confirms that the re-orientation of the particles
does not disrupt the bijel structure but leads to partial alignment of
the interfaces without changing the general topology of the bicontinuous
morphology.

When the particles rotate, the interface exerts a capillary torque on
the particles due to the surface tension and the contact angle. If the
magnetic torque exceeds the interfacial forces, the particles can
potentially overcome the capillary torque and rotate out of the
interface. For prolate particles (\(\alpha=2\)) adsorbed at flat
interfaces, Davies et al. have shown that a transition between the
energetically preferred ``flat'' orientation and a tilted orientation
occurs at a critical field strength of approximately \(\bar{B}=0.2\)
\cite{bresme_orientational_2007,davies_interface_2014,newton_influence_2014}.
In the case of bijels, however, the percolating interfaces are tortuous
and thus more mobile. We therefore posit that, rather than tilting out
of the interface, rotating particles can ``pull'' the interface along
and thereby align the liquid domains. For anisotropic particles, we
expect that the interfaces align along the larger cross-section of the
particles, i.e., perpendicular to the symmetry axis of oblate particles
and parallel to the symmetry axis of prolate particles. The data for the
anisotropic domain size and tortuosity above is consistent with this
assumption. To ascertain that the particles remain indeed in their
energetically preferred orientation with respect to the interface, we
analyzed the angle between the symmetry axis of the particles and the
interface normal calculated using the technique defined in Section 
\ref{section:interface_angle}. Figure \ref{fig:psi_time} shows the time-dependence of the average angle
\(\psi\) between the particle dipole axis and the nearest interface normal.

@@

For both types of anisotropic particles, the average angle between the
particle dipole and the interface normal is initially around
\(\psi\approx60^\circ\). As the spinodal interface sweeps through the
system, particles attach to the interface and alignment due to the
capillary torque sets in. For oblate particles, the dipole axis aligns
with the interface normal as indicated by the decay of \(\psi\) towards
zero. For prolate particles, the preferential alignment of the dipole
axis is parallel to the interface and hence \(\psi\) increases towards
\(90^\circ\). The main variation of \(\psi\) occur in a time interval
around \(10^4\Delta t\) which coincides with the distinct features of
the coarsening speed and the particle nematic order observed above. The
results thus substantiate the proposed mechanism of particle
re-orientation in the magnetic field and the concomitant local alignment
of the interface. Once the particles start jamming, the shrinking
interfacial area forces some particles out of their preferred alignment
with the interface, leading to an increase of \(\psi\) for oblate
particles and a decrease of \(\psi\) for prolate particles. Figure
\ref{fig:psi_time} suggests that the forced tilting is more pronounced
for oblate particles than for prolate particles. Due to the larger
aspect ratio, the tilting of prolate particles relative to the interface
induces deformations that appear to cause a larger capillary torque than
the tilting of oblate particles. %For oblate particles, the liquid-solid
%contact line is on average further away from the particle center than
%for prolate particles, hence the lever effect of oblate particles is
%weaker and allows larger tilting relative to the the preferred alignment
%with the interface.
Hence the prolate particles remain mostly aligned with the interface
even in the stronger applied magnetic fields. We plot the interface angle of bijels
stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
that the application of magnetic fields have on the particle monolayer.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/results/paper1/rdf_compare_time.png}
\caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic 
        field strength $\bar{B}$. The radial distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps. 
        The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ of the larger particle axis. The peaks 
        illustrate the packing of particles in the interface. Dashed lines indicate the side-by-side, tip-to-tip, 
        and side-to-tip configuration of particle pairs. For spherical particles, the three values are identical. 
        The insets show snapshots of the particle arrangement with and without magnetic field at the respective timesteps. 
        The direction of the magnetic field is indicated by arrows.}
\label{fig:rdf}
\end{figure*}

>>>>

@@

Bijels serve as emulsion templates for fabricating porous materials with applications in areas such as drug delivery, water purification, and energy 
storage devices like battery electrodes \cite{vanoli_bijels_2022, chen_pore-scale_2022, lu_controllable_2020, garcia_scalable_2019}. The performance of
materials in these applications are influenced by their microstructure. In the following section, the microstructure of magnetically responsive bijels
are assessed. The bijels in our simulations have a particle volume fraction $\phi_p = 0.15$ with magnetic Bond numbers ranging from 
$\bar{Bo} = 0, 0.2, 0.5, 1$. Three simulations per particle and per magnetic field strength are performed, allowing for investigations into the effect of
the initial particle configuration on the obtained microstructure. While properties such as the particle contact angle, fluid ratio, surface tension and
particle volume fraction are important, this study will focus exclusively on the effect of magnetic fields on bijels. 
\cite{jansen_bijels_2011, hijnen_bijels_2015}

\subsection{Microstructure evolution of magnetically responsive bijels}

@@

Figure \ref{fig:microstructure_viz} presents snapshots of the bijel microstructure during formation and at the final timestep with and without magnetic fields.
The figure highlights the alignment of anisotropic particles along the field direction following its application. Particle reorientation leads to apparently larger
domain sizes in the bijels, characterized through magnetic field driven rearrangement of particles at the interface. Past work has identified how droplet coalescence
can be induced through application of magnetic fields. \cite{melle_pickering_2005} This behavior can be quantified using the domain size, done in the following section.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/results/paper1/domain_size.png}
    \caption{Time dependence of the average domain size of the bijel for different particles shapes $\alpha$ and at different magnetic 
             field strength $\bar{B}$. $L_1$ denotes the domain size obtained from the first moment of the spherical average structure 
             factor, and $L_d$ denotes the domain size obtained from the second moment of the 3D structure factor. The increase roughly 
             follows a $\sim t^{2/3}$ scaling law indicative of the inertial regime of spinodal decomposition. Image courtesy of Ulf D. Schiller}
    \label{fig:domain_size}
\end{figure}

Two methods have been identified to characterize the domain size of bijels from the structure factor. They are the first moment of the spherically averaged structure factor
named $L_1$ and the second moment of the directional structure factor. The numerical average of the second moment derived structure factor is named $L_d$. Comparing the time
evolution of both in Figure \ref{fig:domain_size}, the domain size increases before slowing down and finally plateauing. This indicates unhindered spinodal decomposition at
early times, followed by a slowdown of domain coarsening caused by particle interactions before the bijel microstructure jams. Comparing the characterized domain sizes, 
$L_d \~ 80$ compared to $L_1 \~ 150$. $L_d$ and $L_1$ also have differing time evolution, with $L_d$ beginning to plateau earlier than $L_1$. To identify which lengthscale 
should be used to characterize the time evolution of the structure, we invoke dynamical scaling.

From dynamical scaling, spinodal decomposition of binary fluids can be characterized through the inertial regime $L \~ t^{2/3}$, crossover regime $L \~ t^{n}, 2/3 < n < 1$ and 
the inertial regime $L \~ t$. \cite{kendon_3d_1999,kendon_inertial_2001} These scaling regimes can be obtained from the Navier Stokes equation with additional surface tension 
forces. The characterized lengthscales should conform to dynamical scaling as it is independent of the method used to characterize the lengthscale. By fitting the first phase
of the domain size evolution for all particle shapes, the scaling exponent of domain size change characterized with $L_1$ is found to be approximately $L \~ t^{2/3}$. However
the scaling exponent for $L_d$ is found to be $L \~ t^{0.2}$. Therefore, $L_1$ is selected to characterize the time evolution of the domain size. However the second moment of
the domain size allows characterization of the domain size in each cartesian direction. The second moment derived domain size will be used to characterize the microstructure
of the bijel.

\subsection{Effect of magnetic field on bijel microstructure}

% In LB simulations of spinodal decomposition, a characteristic length
% scale can be obtained from the structure factor, defined in Section \ref{section:domain_size}. \cite{kendon_3d_1999,kendon_inertial_2001} 
% It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
% domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
% scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
% used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
% averaged structure factor is subject to poor statistics in the low \(k\)-shells, where the average \(|\vec{k}|\) of the 
% lattice sites differs from the nominal shell radius. Additionally, the measurement of \(L(t)\) in simulations with
% periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
% We cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
% size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
% \cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
% from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ we plot the structure factor of the structures in
% Figure \ref{fig:structure_factor}.

@@

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.4]{figures/results/paper1/tortuosity_compare.png}
    \caption{Dependence of the tortuosity on the magnetic field strength $\bar{B}$ for different particle shapes $\alpha$. 
             Different components of the tortuosity tensor show the anisotropy for oblate and prolate particles.}
    \label{fig:tau_B}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/results/paper1/coarsening_vel.png}
\caption{Time-dependence of the coarsening velocity $u_L$ for different particles shapes $\alpha$  
and at different magnetic field strength $\bar{B}$. The different components of the coarsening velocity 
show that the jamming time is different in the direction parallel and perpendicular to the magnetic field. Image provided
courtesy of Ulf D. Schiller.}
\label{fig:coarsening_velocity}
\end{figure}

% Figure \ref{fig:coarsening_velocity} shows the coarsening speed in the directions parallel and perpendicular to the applied magnetic field. 
% The data confirms that for spherical particles, domain coarsening remains isotropic. We observe a higher coarsening speed initially which slows 
% at later times when the particles begin to jam. This indicates that the
% coarsening is subject to different time scales, as reported previously
% by Harting and co-workers \cite{gunther_timescales_2014}. Reeves et
% al.~\cite{reeves_particle-size_2015} have pointed out that bijel
% formation hinges on the jamming time in relation to the disruption time, i.e., the time scale at which domain pinch-off events can cause bijel break-up through 
% depercolation. In our simulations, however, we have not observed disruption of bijel formation; stable bijels form for all parameters consistent with simulations 
% by Stratford et
% al.~\cite{stratford_colloidal_2005} and Jansen et al.~\cite{jansen_bijels_2011}.

% For ellipsoidal particles, our data clearly shows that an\-isotropic
% domain coarsening arises in magnetic fields.  For oblate particles
% (\(\alpha=0.5\)), the coarsening speed in the direction perpendicular
% to the field increases with increasing magnetic field strength.
% Jamming in this direction appears to be delayed compared with the
% direction parallel to the field. The coarsening speed in the parallel
% direction remains comparable to the case without an applied magnetic
% field. This anisotropic behavior of the coarsening speed reverses for
% prolate particles, where the coarsening speed in the direction parallel to the field increases with increasing field strength, and jamming in this direction
% is delayed compared with the perpendicular direction. In addition, we observe a shoulder (around \(10^4\Delta t\)) where the coarsening speed decays more slowly before jamming sets in. These results suggest that the coarsening near the jamming time is affected by a mechanism that depends on the applied magnetic field and causes the anisotropic
% behavior. This mechanisms involves the re-orientation of anisotropic
% particles and their alignment relative to the direction of the
% magnetic field. To confirm this hypothesis, we analyze the
% orientational order of the particles and their alignment relative to
% the magnetic field and the interface, respectively.

@@

@@

@@

Hence the prolate particles remain mostly aligned with the interface
even in the stronger applied magnetic fields. We plot the interface angle of bijels
stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
that the application of magnetic fields have on the particle monolayer.

Hence the prolate particles remain mostly aligned with the interface
even in the stronger applied magnetic fields. We plot the interface angle of bijels
stabilized by ellipsoidal particles at the final timestep to demonstrate the differences
that the application of magnetic fields have on the particle monolayer.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/results/paper1/rdf_compare_time.png}
\caption{Time-evolution of the radial distribution function $g(r)$ of the particles at different magnetic 
        field strength $\bar{B}$. The radial distribution function is shown at $10^3$, $10^4$, and $10^5$ timesteps. 
        The distance $r$ is normalized by the radius $R=\max(R_\parallel,R_\perp)$ of the larger particle axis. The peaks 
        illustrate the packing of particles in the interface. Dashed lines indicate the side-by-side, tip-to-tip, 
        and side-to-tip configuration of particle pairs. For spherical particles, the three values are identical. 
        The insets show snapshots of the particle arrangement with and without magnetic field at the respective timesteps. 
        The direction of the magnetic field is indicated by arrows.}
\label{fig:rdf}
\end{figure}
